On the minimum leaf conductance g~0~

### 2017-03-30 manuscript.Rmd
adjusted some figures

The g~0~ parameter is the intercept, i.e. g~s~ when A is zero. Depending on the form of f(D), it can also represent g~s~ when D is very large.

The objective of this paper is to review sources of variation and common misconceptions on the g~0~ parameter.

@@

@manzoni2011 assumes minimum conductance is cuticular only, because CO2 does not diffuse across it but water does. Seems to work in his modelling context but appears to be in disagreement with the observation that gmin >> gcut.

@kala2016 g0 effect heat waves etc.

@@

The first Ball-Berry model did not have a g0

@leuning1995 says "g0 > 0, otherwise ci/ca would be constant for all values of Q. The rate of convergence of ci to ca at low A (low Q) depends on the value of g0; when g0 is large, ci deviates from the asymptotic value at higher values of A than when g0 is small".

@@

similarly at high T. See also Kala. Figure 1.

@@

@dekauwe2015 makes this point as well, their Fig. A2 (can we add that also?)

@@

We compare estimates of g~cut~, g~min~, and g~dark~ from the literature. Measurements of g~cut~ and g~min~ were taken from the compilation by @kerstiens1996, with additional g~min~ measurements from @schuster2016, @burghardt2003, @cavenderbares2007, and @phillips2010 (for the latter study, raw data were obtained and g~min~ calculated). It is customary for g~cut~ and g~min~ to be expressed per unit total leaf surface area, however, since we aim a comparison with g~s~ and g~dark~, all values were converted to per unit projected surface area. Units were converted to molar fluxes assuming 41 mol m^-3^ (cf. @kerstiens1996). For g~dark~, we used a recent compilation of measurements from @lombardozzi2017.

@@

@waldencoleman2013 gdark is much higher than gmin. Whole-plant WUE correlated with gdark (but not gmin). Lots of references on gdark and gmin and their variation. Closed system to measure gdark+gmin; gmin on detached leaves.

@@

**Figure 4**. Comparison of various estimates of minimum conductance. Error bars are standard errors, grey vertical lines 90% quantiles indicating wide range of variation for any variable. g~cut,isol~ : cuticual permeance measured on isolated cuticles that lack stomata (data from Kerstiens 1996), g~min,seal~ : minimum conductance based on leaf dry-down curves where the side of the leaf that bears stomata is sealed (data from Kerstiens 1996), g~min~ : minimum conductance based on leaf-dry-down curves (data from Kerstiens 1996, with a few extra data points - to be added), g~dark : stomatal conductance in the dark at night, measured in field conditions (data from Lombardozzi et al. 2017), g~0~ : fitted g~0~ in the Medlyn et al. (2011) model with the Lin et al. (2015) database, g~s,low A~ : for the Lin et al. (2015) database, minimum g~s~ when net assimilation rate was less than 2 $mu$ mol m^-2^ s^-1^, calculated once for each dataset. Minimum conductance and cuticular conductance are commonly expressed per all surface area but here projected was used because that's more common for g0, gdark.

>>>>

The origin of Eq. 1 is @ball1987 , but no g~0~ was mentioned. It is introduced in the unpublished manuscript of @ball1988, as an 'intercept' without further discussion of the role it plays in the model.

@leuning1990 defined g~0~ as g~s~ when A approaches zero as PPFD approaches the light compensation point, and also points out that it plays a role in predicting A/g~s~ (and C~i~) at low light [see also @leuning1995].

@@

Though the role and potential for estimation using Eq. 1 is clear, it is not clear whether and how g~0~ compares to other estimates of g~s~ when photosynthesis is zero. It is sometimes assumed that g~0~ must equal g~s~ at night, simply since no photosynthesis occurs at night [@lombardozzi2016; @barnard2013]. Other studies assume that g~0~ equals a 'cuticular conductance` [@manzoni2011; @egea2011], but it has yet to be determined how various minimum conductance estimates compare.

The objective of this paper is to take a closer look at g~0~, its role in modelling fluxes of carbon and water, estimation of g~0~ from regression of Eq. 1 against data. Finally we review the literature for sources of variation in the actual minimum conductance measured in various ways. On the way we try to set straight some common misconceptions about g~0~, and make recommendations for future work.

@@

@leuning1990 and @leuning1995 says "g0 > 0, otherwise ci/ca would be constant for all values of Q. The rate of convergence of ci to ca at low A (low Q) depends on the value of g0; when g0 is large, ci deviates from the asymptotic value at higher values of A than when g0 is small".

@@

similarly at high T. @kala2016 @urban 
drake in prep
duursma2014

@@

@@

We compare estimates of g~cut~, g~min~, and g~dark~ from the literature. Measurements of g~cut~ and g~min~ were taken from the compilation by @kerstiens1996, with additional g~min~ measurements from @schuster2016, @burghardt2003, @cavenderbares2007, and @phillips2010 (for the latter study, raw data were obtained and g~min~ calculated). We excluded measurements of g~min~ where stomatal leaf sides were sealed, because few data were available and the comparison is not consistent with individual studies where the role of stomata in g~min~ is studied (see SectionXXX).

It is customary for g~cut~ and g~min~ to be expressed per unit total leaf surface area, however, since we aim a comparison with g~s~ and g~dark~, all values were converted to per unit projected surface area. Units were converted to molar fluxes assuming 41 mol m^-3^ (cf. @kerstiens1996). For g~dark~, we used a recent compilation of measurements from @lombardozzi2017.

@@

g~s,minA~ calculated from @lin2015 data. Also g0 fitted using the model of Medlyn et al. 2011, and those from @miner2016 (combined all).

g~s,low A~ much lower than fitted g~0~ or g~dark~ (see also @dekauwe2015, their Fig. A2).

g~dark~ much higher than g~min~, also confirmed by experiments. In soybean, @waldencoleman2013 showed much higher g~dark~  compared to g~min~.

@@

**Figure 4**. Comparison of various estimates of minimum conductance. Error bars are standard errors, grey vertical lines 90% quantiles indicating wide range of variation for any variable. g~cut,isol~ : cuticual permeance measured on isolated cuticles that lack stomata (data from Kerstiens 1996), g~min~ : minimum conductance based on leaf-dry-down curves (data from Kerstiens 1996, with a few extra data points - to be added), g~dark : stomatal conductance in the dark at night, measured in field conditions (data from Lombardozzi et al. 2017), g~0~ : fitted g~0~ in the Medlyn et al. (2011) model with the Lin et al. (2015) database, g~s,low A~ : for the Lin et al. (2015) database, minimum g~s~ when net assimilation rate was less than 2 $mu$ mol m^-2^ s^-1^, calculated once for each dataset. Minimum conductance and cuticular conductance are commonly expressed per all surface area but here projected was used because that's more common for g0, gdark.
